Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors

### 2018-08-01 main.tex
Final version

\begin{figure}[ht]
    \centering
    \subfloat[The real part of arccotangent with a branch cut at ${[-\iunit\infty, -\iunit]}$, ${[\iunit,\iunit\infty]}$.]{        \includegraphics[width=0.45\textwidth]{acotCut1.png}
        \label{fig:acot-cut1}    }
    \hspace{0.5cm}
    \subfloat[The real part of arccotangent with a branch cut at ${[-\iunit, \iunit]}$.]{        \includegraphics[width=0.45\textwidth]{acotCut2.png}
        \label{fig:acot-cut2}    }
    \caption{Two plots for the real part of the arccotangent function with a branch cut at $[-\iunit\infty, -\iunit]$, $[\iunit,\iunit\infty]$ in Figure~\protect\subref{fig:acot-cut1} and at $[-\iunit, \iunit]$ in Figure~\protect\subref{fig:acot-cut2}, respectively. (Plotted with \Maple{} 2016)}
    \label{fig:acot-cut-compare}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \subfloat[The real part of arccotangent with a branch cut at ${[-\iunit\infty, -\iunit]}$, ${[\iunit,\iunit\infty]}$.]{
    		\includegraphics[width=0.45\textwidth]{acotCut1.jpg}
        \label{fig:acot-cut1}
    }
    \hspace{0.5cm}
    \subfloat[The real part of arccotangent with a branch cut at ${[-\iunit, \iunit]}$.]{
    		\includegraphics[width=0.45\textwidth]{acotCut2.jpg}
        \label{fig:acot-cut2}
    }
    \caption{Two plots for the real part of the arccotangent function with a branch cut at $[-\iunit\infty, -\iunit]$, $[\iunit,\iunit\infty]$ in Figure~\protect\subref{fig:acot-cut1} and at $[-\iunit, \iunit]$ in Figure~\protect\subref{fig:acot-cut2}, respectively. (Plotted with \Maple{} 2016)}
    \label{fig:acot-cut-compare}
\end{figure}
